\input cwebmac
% ttt.w -- Tic tac toe game in CWEB, Copyright (c) 2015 Andrew A. Cashner
% 2015-05-26


\N{1}{1}Introduction. This is \.{ttt}, a command-line tic-tac-toe game.
% TODO more

\Y\B\8\#\&{include} \.{<stdio.h>}\6
\8\#\&{include} \.{<stdlib.h>}\6
\8\#\&{include} \.{<string.h>}\6
\X2:Global variables\X\7
\&{typedef} \&{enum} ${}\{{}$\1\6
${}\.{FALSE},\39\.{TRUE}{}$\2\6
${}\}{}$ \&{boolean};\7
\X10:Function prototypes\X\7
\&{int} \\{main}(\&{int} \\{argc}${},\39{}$\&{char} ${}{*}\\{argv}[\,]){}$\1\1%
\2\2\6
${}\{{}$\1\6
\X3:Main variables\X\7
\&{boolean} \\{bool\_gameover};\7
${}\\{bool\_gameover}\K\.{FALSE};{}$\6
\X7:Populate switching tables\X\6
${}\\{printf}(\.{"\%s\\n"},\39\\{greeting});{}$\6
\X4:Draw board\X\6
\&{while} ${}(\\{bool\_gameover}\E\.{FALSE}){}$\5
${}\{{}$\1\6
\X14:Get O move, update board\X\6
\X16:Check for O win\X\6
\X17:Prepare next move\X\6
\4${}\}{}$\2\6
\X26:Gameover routine\X\6
\&{return} (\T{0});\6
\4${}\}{}$\2\par
\fi

\N{1}{2}Printing the game board.
Set up switching tables needed to draw the board, and update the drawing.

\Y\B\4\X2:Global variables\X${}\E{}$\6
\&{static} \&{const} \&{int} \\{charboard\_index}[\,]${}\K\{{}$\6
${}\T{2},\39\T{6},\39\T{10},{}$\6
\T{26}${},\39\T{30},\39\T{34},{}$\6
\T{50}${},\39\T{54},\39{}$\T{58}\6
${}\};{}$\6
\&{static} \&{const} \&{enum} ${}\{{}$\1\6
${}\.{A1},\39\.{A2},\39\.{A3},{}$\6
\.{B1}${},\39\.{B2},\39\.{B3},{}$\6
\.{C1}${},\39\.{C2},\39\.{C3}{}$\2\6
${}\}{}$ \\{squareID};\6
\&{static} \&{const} \&{char} ${}{*}\\{square\_label}[\,]\K\{{}$\6
${}\.{"A1"},\39\.{"A2"},\39\.{"A3"},{}$\6
\.{"B1"}${},\39\.{"B2"},\39\.{"B3"},{}$\6
\.{"C1"}${},\39\.{"C2"},\39{}$\.{"C3"}\6
${}\};{}$\6
\&{static} \&{const} \&{enum} ${}\{{}$\1\6
${}\.{EMPTY},\39\.{XPLAYER},\39\.{OPLAYER}{}$\2\6
${}\}{}$ \\{playerID};\6
\&{static} \&{const} \&{char} \\{playerchar}[\,]${}\K\{\.{'\ '},\39\.{'X'},\39%
\.{'O'}\}{}$;\par
\As5, 8, 19, 25\ETs27.
\U1.\fi

\M{3}We set up the table within \PB{\\{main}}.
\PB{\\{gameboard}} holds \PB{\&{int}} values for each square of the gameboard,
which is either
\PB{\.{EMPTY}}, \PB{\.{XPLAYER}}, or \PB{\.{OPLAYER}}.
\PB{\\{charboard}} holds the characters to draw the board, and will be updated
as new
squares of \PB{\\{gameboard}} are filled.

\Y\B\4\D$\.{CHAR\_BOARD\_LENGTH}$ \5
\T{62}\par
\Y\B\4\X3:Main variables\X${}\E{}$\6
\&{int} \\{gameboard}[\T{9}]${}\K\{\T{0},\39\T{0},\39\T{0},\39\T{0},\39\T{0},%
\39\T{0},\39\T{0},\39\T{0},\39\T{0}\}{}$;\C{ Start empty }\6
\&{char} \\{charboard}[\,]${}\K{}$\6
\.{"\\n\ \ \ |\ \ \ |\ \ \ \\n"}\6
\.{"-----------\\n"}\6
\.{"\ \ \ |\ \ \ |\ \ \ \\n"}\6
\.{"-----------\\n"}\6
\.{"\ \ \ |\ \ \ |\ \ \ \\n\\n"};\6
\&{int} ${}{*}\\{gameboard\_ptr}\K\\{gameboard};{}$\6
\&{char} ${}{*}\\{charboard\_ptr}\K\\{charboard}{}$;\par
\As6, 13\ETs15.
\U1.\fi

\M{4}Draw the board. We simply print \PB{\\{charboard}} to \PB{\\{stdout}}.

\Y\B\4\X4:Draw board\X${}\E{}$\6
$\\{printf}(\.{"\%s"},\39\\{charboard}){}$;\par
\Us1, 14\ETs17.\fi

\N{1}{5}Test for winning combinations.
Set up a switching table with the winning triple series.
Set up a table of permutations of these triples in which the first two are in
ascending order (to find runs of 2/3).

\Y\B\4\D$\.{MAXANSWERS}$ \5
\T{8}\par
\Y\B\4\X2:Global variables\X${}\mathrel+\E{}$\6
\&{static} \&{const} \&{int} \\{answer}[\T{8}][\T{3}]${}\K\{{}$\6
${}\{\T{0},\39\T{1},\39\T{2}\},{}$\6
${}\{\T{0},\39\T{3},\39\T{6}\},{}$\6
${}\{\T{0},\39\T{4},\39\T{8}\},{}$\6
${}\{\T{1},\39\T{4},\39\T{7}\},{}$\6
${}\{\T{2},\39\T{4},\39\T{6}\},{}$\6
${}\{\T{2},\39\T{5},\39\T{8}\},{}$\6
${}\{\T{3},\39\T{4},\39\T{5}\},{}$\6
${}\{\T{6},\39\T{7},\39\T{8}\}{}$\6
${}\}{}$;\par
\fi

\M{6}Set up switching table of permutations; we have to do this in \PB{%
\\{main}}.

\Y\B\4\D$\.{MAXPERMS}$ \5
\T{24}\par
\Y\B\4\X3:Main variables\X${}\mathrel+\E{}$\6
\&{int} \\{perms}[\.{MAXPERMS}][\T{3}];\C{ Permutations of answer triples where
[0] < [1] }\6
\&{int} \|a${},{}$ \|b${},{}$ \|c;\C{ Single test values }\6
\&{int} \|j;\C{ Loop counter }\par
\fi

\M{7}\B\X7:Populate switching tables\X${}\E{}$\C{ Build table of permutations }%
\6
\&{for} ${}(\|i\K\T{0},\39\|j\K\T{0};{}$ ${}\|i<\.{MAXANSWERS};{}$ ${}\PP%
\|i){}$\5
${}\{{}$\1\6
${}\|a\K\\{answer}[\|i][\T{0}];{}$\6
${}\|b\K\\{answer}[\|i][\T{1}];{}$\6
${}\|c\K\\{answer}[\|i][\T{2}];{}$\6
${}\\{perms}[\|j][\T{0}]\K\|a;{}$\6
${}\\{perms}[\|j][\T{1}]\K\|b;{}$\6
${}\\{perms}[\|j][\T{2}]\K\|c;{}$\6
${}\PP\|j;{}$\6
${}\\{perms}[\|j][\T{0}]\K\|a;{}$\6
${}\\{perms}[\|j][\T{1}]\K\|c;{}$\6
${}\\{perms}[\|j][\T{2}]\K\|b;{}$\6
${}\PP\|j;{}$\6
${}\\{perms}[\|j][\T{0}]\K\|b;{}$\6
${}\\{perms}[\|j][\T{1}]\K\|c;{}$\6
${}\\{perms}[\|j][\T{2}]\K\|a;{}$\6
${}\PP\|j;{}$\6
\4${}\}{}$\2\par
\U1.\fi

\N{1}{8}Create linked lists of each player's current board positions.
We will insert new moves into list of moves for a particular player, keeping
the list sorted in ascending order.

\Y\B\4\X2:Global variables\X${}\mathrel+\E{}$\6
\&{typedef} \&{struct} \\{square} ${}{*}\&{square\_ptr};{}$\6
\&{typedef} \&{struct} \&{square} ${}\{{}$\1\6
\&{int} \\{position};\6
\&{square\_ptr} \\{next};\2\6
${}\}{}$ \&{square};\par
\fi

\M{9}Function to insert items into linked list.

\Y\B\&{square\_ptr} \\{insert\_sorted}(\&{square\_ptr} \\{head}${},\39{}$%
\&{int} \\{new\_position})\1\1\2\2\6
${}\{{}$\1\6
\&{square\_ptr} \\{list};\6
\&{square\_ptr} \\{new\_square}${}\K\\{malloc}(\&{sizeof}(\&{square\_ptr}));{}$%
\7
${}\\{new\_square}\MG\\{position}\K\\{new\_position};{}$\6
${}\\{new\_square}\MG\\{next}\K\NULL{}$;\C{ Create new list if there is none }\6
\&{if} ${}(\\{head}\E\NULL){}$\5
${}\{{}$\1\6
${}\\{list}\K\\{new\_square};{}$\6
\&{return} (\\{list});\6
\4${}\}{}$\2\6
\&{else}\5
${}\{{}$\1\6
${}\\{list}\K\\{head};{}$\6
\4${}\}{}$\C{ If new position is less, put at head of list and return head }\2\6
\&{if} ${}(\\{new\_position}<\\{list}\MG\\{position}){}$\5
${}\{{}$\1\6
${}\\{new\_square}\MG\\{next}\K\\{list};{}$\6
\&{return} (\\{new\_square});\6
\4${}\}{}$\C{ Loop through to find mid-list insertion point }\2\6
\&{while} ${}(\\{list}\MG\\{next}\I\NULL){}$\5
${}\{{}$\1\6
\&{if} ${}(\\{new\_position}<(\\{list}\MG\\{next})\MG\\{position}){}$\5
${}\{{}$\C{ Insert the node mid-list, here }\1\6
${}\\{new\_square}\MG\\{next}\K\\{list}\MG\\{next};{}$\6
${}\\{list}\MG\\{next}\K\\{new\_square};{}$\6
\&{return} (\\{head});\6
\4${}\}{}$\2\6
\&{else}\5
${}\{{}$\1\6
${}\\{list}\K\\{list}\MG\\{next};{}$\6
\4${}\}{}$\2\6
\4${}\}{}$\C{ If node is greatest of all, add it to end of list }\2\6
${}\\{list}\MG\\{next}\K\\{new\_square};{}$\6
${}\\{new\_square}\MG\\{next}\K\NULL{}$;\C{ Return head of list }\6
\&{return} (\\{head});\6
\4${}\}{}$\2\par
\fi

\M{10}\B\X10:Function prototypes\X${}\E{}$\6
\&{square\_ptr} \\{insert\_sorted}(\&{square\_ptr} \\{head}${},\39{}$\&{int} %
\\{new\_position});\par
\As12, 22\ETs24.
\U1.\fi

\N{1}{11}Updating the game board.

\Y\B\&{int} \\{newmove}(\&{int} \\{player}${},\39{}$\&{int} \\{position}${},%
\39{}$\&{int} ${}{*}\\{gameboard},\39{}$\&{char} ${}{*}\\{charboard}){}$\1\1\2%
\2\6
${}\{{}$\1\6
${}{*}(\\{gameboard}+\\{position})\K\\{player};{}$\6
${}{*}(\\{charboard}+\\{charboard\_index}[\\{position}])\K\\{playerchar}[%
\\{player}];{}$\6
\&{return} (\T{0});\6
\4${}\}{}$\2\par
\fi

\M{12}\B\X10:Function prototypes\X${}\mathrel+\E{}$\6
\&{int} \\{newmove}(\&{int} \\{player}${},\39{}$\&{int} \&{square}${},\39{}$%
\&{int} ${}{*}\\{gameboard},\39{}$\&{char} ${}{*}\\{charboard}){}$;\par
\fi

\N{1}{13}Get user input for O move.

\Y\B\4\D$\.{MAXLINE}$ \5
\T{100}\par
\Y\B\4\X3:Main variables\X${}\mathrel+\E{}$\6
\&{char} \\{input\_line}[\.{MAXLINE}];\6
\&{int} \\{nextOmove};\6
\&{int} \\{squares\_filled};\C{ Total squares filled on board }\6
\&{square\_ptr} \\{listOmoves}${}\K\NULL;{}$\6
\&{int} \\{total\_O\_moves}${}\K\T{0};{}$\6
\&{int} \\{total\_X\_moves}${}\K\T{0}{}$;\C{ Counter per player of moves on
board }\6
\&{int} \\{winner}${}\K\.{EMPTY}{}$;\par
\fi

\M{14}Check O command for validity and set \PB{\\{nextOmove}}.
The command is entered in the form \.{A1\\n}.
\.{'A'} is 0, \.{'B'} is 3, \.{'C'} is 6.
\.{'A1'} is $0 + 0$, \.{'B2'} is $3 + 1$.

\Y\B\4\X14:Get O move, update board\X${}\E{}$\6
\&{while} (\T{1}) $\{{}$\7
\\{printf}(\.{"\\nYour\ move?\\n"});\6
${}\\{fgets}(\\{input\_line},\39{}$\&{sizeof} (\\{input\_line})${},\39%
\\{stdin}){}$;\7
\&{if} ${}(\\{input\_line}[\T{2}]\I\.{'\\n'}\V\\{input\_line}[\T{0}]<\.{'A'}\V%
\\{input\_line}[\T{0}]>\.{'C'}\V\\{input\_line}[\T{1}]<\.{'1'}\V\\{input%
\_line}[\T{1}]>\.{'3'})$ $\{$ \\{printf} $(\.{"\%s\\n"},\39$ \&{error} [\.{O%
\_COMMAND\_OUT\_OF\_RANGE}] )  ;\5
\&{continue}; $\}{}$\7
$\\{nextOmove}\K(\\{input\_line}[\T{0}]-\.{'A'})*\T{3};{}$\6
${}\\{nextOmove}\MRL{+{\K}}\\{input\_line}[\T{1}]-\.{'1'};$ \6
\&{if} ${}(\\{gameboard}[\\{nextOmove}]\E\.{EMPTY}){}$\5
${}\{{}$\1\6
${}\\{newmove}(\.{OPLAYER},\39\\{nextOmove},\39\\{gameboard\_ptr},\39%
\\{charboard\_ptr});{}$\6
\X4:Draw board\X\6
${}\PP\\{squares\_filled};{}$\6
${}\PP\\{total\_O\_moves};{}$\6
${}\\{listOmoves}\K\\{insert\_sorted}(\\{listOmoves},\39\\{nextOmove});{}$\6
\\{printf}(\.{"O\ moves:\ "});\6
\\{print\_movelist}(\\{listOmoves});\6
\&{break};\6
\4${}\}{}$\2\6
\&{else} $\{$ \\{printf} $(\.{"\%s\\n"},\39$ \&{error} [\.{SQUARE\_OCCUPIED}] )
 ; $\}{}$\7
$\}{}$\par
\U1.\fi

\N{1}{15}Process the X and O moves of turn just completed, and prepare next X
move.

\Y\B\4\X3:Main variables\X${}\mathrel+\E{}$\6
\&{int} \\{best\_moves}[\,]${}\K\{\.{B2},\39\.{A1},\39\.{A3},\39\.{C1},\39%
\.{C3},\39\.{A2},\39\.{B1},\39\.{B3},\39\.{C2}\};{}$\6
\&{int} \\{total\_best\_moves}${}\K\T{8};{}$\6
\&{int} \|i;\6
\&{square\_ptr} \\{listXmoves}${}\K\NULL;{}$\6
\&{int} \\{nextXmove};\6
\&{int} \\{test};\par
\fi

\M{16}See if O wins by having three in a row.

\Y\B\4\X16:Check for O win\X${}\E{}$\6
\&{if} ${}(\\{total\_O\_moves}>\T{2}){}$\5
${}\{{}$\1\6
${}\\{test}\K\\{two\_of\_three}(\.{OPLAYER},\39\\{listOmoves},\39\\{perms},\39%
\\{gameboard\_ptr});{}$\6
\&{if} ${}(\\{test}\E\.{O\_WINS}){}$\5
${}\{{}$\1\6
${}\\{bool\_gameover}\K\.{TRUE};{}$\6
${}\\{winner}\K\.{OPLAYER};{}$\6
\4${}\}{}$\2\6
\4${}\}{}$\2\par
\U1.\fi

\M{17}Prepare next move.
Test O values for 3/3; if so, O wins.
If not, check if X has 2/3; if so, move to missing 3rd spot to win.
If there is no 2/3 run for X, check if O has 2/3 and move to third spot to
block
O from winning.
If there is no 2/3 run for O or X, then choose any favored free spot from
\PB{\\{best\_moves}}.
Finally, add \PB{\\{nextXmove}} to the list of X moves and update the board.
If all the squares are filled, the game is over automatically.

\Y\B\4\X17:Prepare next move\X${}\E{}$\6
\&{if} ${}(\\{total\_X\_moves}<\T{1}){}$\5
${}\{{}$\1\6
\X18:Pick any free spot\X\6
\4${}\}{}$\2\6
\&{else}\5
${}\{{}$\1\6
${}\\{test}\K\\{two\_of\_three}(\.{XPLAYER},\39\\{listXmoves},\39\\{perms},\39%
\\{gameboard\_ptr});{}$\6
\&{if} ${}(\\{test}\I\.{NOTFOUND}){}$\5
${}\{{}$\1\6
\\{printf}(\.{"I\ found\ a\ matching\ }\)\.{triple\ of\ X\ position}\)\.{s.%
\\n"});\6
${}\\{nextXmove}\K\\{test};{}$\6
${}\\{bool\_gameover}\K\.{TRUE};{}$\6
${}\\{winner}\K\.{XPLAYER};{}$\6
\4${}\}{}$\2\6
\&{else}\5
${}\{{}$\1\6
${}\\{test}\K\\{two\_of\_three}(\.{XPLAYER},\39\\{listOmoves},\39\\{perms},\39%
\\{gameboard\_ptr});{}$\6
\&{if} ${}(\\{test}\I\.{NOTFOUND}){}$\5
${}\{{}$\1\6
\\{printf}(\.{"I\ found\ a\ matching\ }\)\.{duple\ of\ O\ positions}\)\.{\ and\
I\ will\ block\ th}\)\.{e\ win.\\n"});\6
${}\\{nextXmove}\K\\{test};{}$\6
\4${}\}{}$\2\6
\&{else}\5
${}\{{}$\1\6
\X18:Pick any free spot\X\6
\4${}\}{}$\2\6
\4${}\}{}$\2\6
\4${}\}{}$\2\6
${}\\{newmove}(\.{XPLAYER},\39\\{nextXmove},\39\\{gameboard\_ptr},\39%
\\{charboard\_ptr});{}$\6
\X4:Draw board\X\6
${}\PP\\{squares\_filled};{}$\6
${}\PP\\{total\_X\_moves};{}$\6
${}\\{listXmoves}\K\\{insert\_sorted}(\\{listXmoves},\39\\{nextXmove});{}$\6
\\{printf}(\.{"X\ moves:\ "});\6
\\{print\_movelist}(\\{listXmoves});\6
\&{if} ${}(\\{squares\_filled}>\T{8}){}$\5
${}\{{}$\1\6
${}\\{bool\_gameover}\K\.{TRUE};{}$\6
${}\\{winner}\K\.{EMPTY};{}$\6
\4${}\}{}$\2\par
\U1.\fi

\M{18}Choose any available free position from a list arranged with the most
optimal
spots (the middle and corners) first.

\Y\B\4\X18:Pick any free spot\X${}\E{}$\6
\\{printf}(\.{"I\ found\ no\ matches;}\)\.{\ I\ will\ pick\ any\ goo}\)\.{d\
free\ spot.\\n"});\6
\&{for} ${}(\|i\K\T{0};{}$ ${}\|i<\\{total\_best\_moves};{}$ ${}\PP\|i){}$\5
${}\{{}$\1\6
${}\\{test}\K\\{best\_moves}[\|i];{}$\6
\&{if} ${}(\\{gameboard}[\\{test}]\E\.{EMPTY}){}$\5
${}\{{}$\1\6
${}\\{nextXmove}\K\\{test};{}$\6
\&{break};\6
\4${}\}{}$\2\6
\4${}\}{}$\2\par
\U17.\fi

\N{1}{19}Function to test for two in a row, and if found, return the third
member.

\Y\B\4\X2:Global variables\X${}\mathrel+\E{}$\6
\&{static} \&{const} \&{enum} ${}\{{}$\1\6
${}\.{NOTFOUND}\K{-}\T{10},\39\.{O\_WINS}{}$\2\6
${}\}{}$ \\{function\_errors};\par
\fi

\M{20}If the player tested is \PB{\.{OPLAYER}} then, the function also checks
the
\PB{\\{listOmoves}} to see if \PB{\.{OPLAYER}} has the third member also,
meaning that O wins.
In that case the function returns \PB{\.{O\_WINS}}.
If no series of two is found, it returns \PB{\.{NOTFOUND}}.

\Y\B\&{int} \\{two\_of\_three}(\&{int} \\{player}${},\39{}$\&{square\_ptr} %
\\{head}${},\39{}$\&{int} \\{perms}[\,][\T{3}]${},\39{}$\&{int} ${}{*}%
\\{gameboard}){}$\1\1\2\2\6
${}\{{}$\1\6
\&{int} \|i${},{}$ \|p;\6
\&{int} \\{third};\C{ Third member of triple when first two are found }\6
\&{square\_ptr} \\{list};\7
\&{if} ${}(\\{head}\E\NULL){}$\5
${}\{{}$\1\6
\&{return} (\.{NOTFOUND});\6
\4${}\}{}$\2\6
\&{else}\5
${}\{{}$\1\6
${}\\{list}\K\\{head};{}$\6
\4${}\}{}$\2\6
\&{for} ${}(\|i\K\T{0};{}$ ${}\\{list}\I\NULL;{}$ ${}\\{list}\K\\{list}\MG%
\\{next},\39\PP\|i){}$\5
${}\{{}$\C{ Test values }\1\6
\&{for} ${}(\|p\K\T{0};{}$ ${}\|p<\.{MAXPERMS};{}$ ${}\PP\|p){}$\5
${}\{{}$\C{ $x$ indices of perms}\1\6
\&{if} ${}(\\{list}\MG\\{position}\E\\{perms}[\|p][\T{0}]){}$\5
${}\{{}$\1\6
\&{if} ${}(\\{list}\MG\\{next}\I\NULL\W(\\{list}\MG\\{next})\MG\\{position}\E%
\\{perms}[\|p][\T{1}]){}$\5
${}\{{}$\1\6
${}\\{third}\K\\{perms}[\|p][\T{2}];{}$\6
\X21:Test this permutation\X\6
\4${}\}{}$\2\6
\4${}\}{}$\2\6
\4${}\}{}$\2\6
\4${}\}{}$\2\6
\&{return} (\.{NOTFOUND});\6
\4${}\}{}$\2\par
\fi

\M{21}If we find a pair of the player's board positions that matches one of the
winning permutations, then we test the permutation.
If the player is \PB{\.{OPLAYER}} then we only want to know if the third
position is
already occupied by O, because in that case O wins the game.
If the player is \PB{\.{XPLAYER}}, then the third position is the next X move
if it is
empty.

\Y\B\4\X21:Test this permutation\X${}\E{}$\6
\&{if} ${}(\\{player}\E\.{OPLAYER}){}$\5
${}\{{}$\1\6
\&{if} ${}({*}(\\{gameboard}+\\{third})\E\.{OPLAYER}){}$\5
${}\{{}$\1\6
\&{return} (\.{O\_WINS});\6
\4${}\}{}$\2\6
\&{else}\5
${}\{{}$\1\6
\&{continue};\6
\4${}\}{}$\2\6
\4${}\}{}$\2\6
\&{else}\5
${}\{{}$\1\6
\&{if} ${}({*}(\\{gameboard}+\\{third})\E\.{EMPTY}){}$\5
${}\{{}$\1\6
\&{return} (\\{third});\6
\4${}\}{}$\2\6
\&{else}\5
${}\{{}$\1\6
\&{continue};\C{ Next \PB{\|p} }\6
\4${}\}{}$\2\6
\4${}\}{}$\2\par
\U20.\fi

\M{22}\B\X10:Function prototypes\X${}\mathrel+\E{}$\6
\&{int} \\{two\_of\_three}(\&{int} \\{player}${},\39{}$\&{square\_ptr} %
\\{head}${},\39{}$\&{int} \\{perms}[\,][\T{3}]${},\39{}$\&{int} ${}{*}%
\\{gameboard}){}$;\par
\fi

\M{23}Print current list of moves (for testing purposes only).

\Y\B\&{void} \\{print\_movelist}(\&{square\_ptr} \\{list})\1\1\2\2\6
${}\{{}$\1\6
\&{for} ( ; ${}\\{list}\I\NULL;{}$ ${}\\{list}\K\\{list}\MG\\{next}){}$\5
${}\{{}$\1\6
${}\\{printf}(\.{"\%s\ "},\39\\{square\_label}[\\{list}\MG\\{position}]);{}$\6
\4${}\}{}$\2\6
\\{printf}(\.{"\\n"});\6
\&{return};\6
\4${}\}{}$\2\par
\fi

\M{24}\B\X10:Function prototypes\X${}\mathrel+\E{}$\6
\&{void} \\{print\_movelist}(\&{square\_ptr} \\{list});\par
\fi

\N{1}{25}Game-over routine.

\Y\B\4\X2:Global variables\X${}\mathrel+\E{}$\6
\&{static} \&{const} \&{char} ${}{*}\\{gameover\_msg}[\,]\K\{{}$\6
${}\.{"***\ \ \ DRAW.\ \ \ \ ***"},{}$\6
\.{"***\ \ X\ WINS.\ \ \ ***"}${},{}$\6
\.{"***\ \ O\ WINS.\ \ \ ***"}${},{}$\6
\.{"***\ Game\ over!\ ***"}\6
${}\};{}$\6
\&{static} \&{const} \&{enum} ${}\{{}$\1\6
${}\.{MSG\_DRAW},{}$\6
\.{MSG\_X\_WINS}${},{}$\6
\.{MSG\_O\_WINS}${},{}$\6
\.{MSG\_GAMEOVER}\2\6
${}\}{}$ \\{gameover\_msg\_label};\par
\fi

\M{26}\PB{\\{winner}} will by \PB{\.{EMPTY}}, \PB{\.{XPLAYER}}, or \PB{%
\.{OPLAYER}}; we can use these as indices
to \PB{\\{gameover\_msg}}.

\Y\B\4\X26:Gameover routine\X${}\E{}$\6
$\\{printf}(\.{"\\n\%s\\n"},\39\\{gameover\_msg}[\.{MSG\_GAMEOVER}]);{}$\6
${}\\{printf}(\.{"\%s\\n\\n"},\39\\{gameover\_msg}[\\{winner}]){}$;\par
\U1.\fi

\N{1}{27}Error messages.

\Y\B\4\X2:Global variables\X${}\mathrel+\E{}$\6
\&{static} \&{const} \&{enum} ${}\{{}$\1\6
${}\.{O\_COMMAND\_OUT\_OF\_RANGE},\39\.{O\_COMMAND\_FAULTY},\39\.{SQUARE%
\_OCCUPIED}{}$\2\6
${}\}{}$ \\{error\_msg}; \&{static} \&{const} \&{char} ${}{*}$ \&{error} [\,] $%
\K$ $\{\.{"That\ square\ is\ not\ }\)\.{on\ the\ board.\ "}\.{"Enter\ A1,\ A2,\
A3,\ B}\)\.{1,\ B2,\ B3,\ C1,\ C2,\ o}\)\.{r\ C3."},\39\.{"I\ don't\ understand%
\ }\)\.{your\ command.\ "}\.{"Enter\ a\ label\ like\ }\)\.{A1\ and\ press\
[ENTER]}\)\.{."},\39\.{"That\ square\ is\ alre}\)\.{ady\ taken.\ Choose\ an}\)%
\.{other."}\};{}$\7
\&{static} \&{const} \&{char} \\{greeting}[\,]${}\K\{\.{"\\nTIC\ TAC\ TOE\\n"}%
\.{"I\ play\ X.\ You\ play\ }\)\.{O.\ You\ go\ first.\\n"}\.{"Use\ one\ of\ the%
\ labe}\)\.{ls\ shown\ below\ to\ sa}\)\.{y\ where\ you\ will\ mov}\)\.{e.\\n"}%
\.{"\\n\ A1\ |\ A2\ |\ A3\ \\n-}\)\.{----------\\n"}\.{"\ B1\ |\ B2\ |\ B3\ %
\\n---}\)\.{--------\\n"}\.{"\ C1\ |\ C2\ |\ C3\\n\\n"}\.{"Let's\ play!"}\}{}$;%
\par
\fi


\inx
\fin
\con
